Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-03-14 manuscript.Rmd
consistent factor orders

# PART 2 AGREEMENT
pt2_group <- read_csv("data/compiled_agreement_position.csv") %>% 
  filter(nap_period == 0 & exclude_period == 0 & !is.na(code) & !is.na(pos)) %>% 
         mutate(pos = factor(pos, levels = pos_levels)) %>% 
  filter(file != "104/1")
pt2_split <- read_csv("data/compiled_agreement_split.csv") %>% 
  filter(nap_period == 0 & exclude_period == 0 & !is.na(code) & !is.na(pos)) %>% 
         mutate(pos = factor(pos, levels = pos_levels)) %>% 
  filter(file != "104/1")

@@

# Count up position totals and join into an agreement data frame
calculate_agreement <- function(ds) {
  model <- ds %>% count(file, pos) %>% 
    add_count(file, wt = n, name = "total") %>% 
    mutate(prop_model = n/total)
  human <- ds %>% count(file, code) %>% 
    add_count(file, wt = n, name = "total") %>% 
    mutate(prop_human = n/total)
  agree_group <- full_join(select(model, file, pos, prop_model), 
                     select(human, file, code, prop_human), 
                     by = c("file" = "file", "pos" = "code"))
  agree_group <- agree_group %>% mutate(prop_human = ifelse(is.na(prop_human), 0, prop_human),
                            prop_model = ifelse(is.na(prop_model), 0, prop_model))
  agree_group <- complete(agree_group, file, pos, fill = list(prop_human = 0, prop_model = 0))
}

@@

agreement_scatter <- function(ds) {
  ggplot() +
  geom_point(data = filter(ds, file %in% outlier_files), mapping = aes(x = prop_human, y = prop_model, shape = file, fill = pos), fill = "#333333", size = 4, alpha = .5) + 
  geom_point(data = filter_outliers(ds), mapping = aes(x = prop_human, y = prop_model, fill = pos), shape = 21, alpha = .5, size = 4) + 
  geom_abline(intercept = 0, slope = 1) + 
  scale_fill_manual(values = pal, guide = "none") + 
  scale_shape_manual(guide = "none", values = 22:23) + 
  scale_x_continuous(breaks = c(0,.5,1), labels = c(0, 50, 100), limits = c(-.07, 1.07), name = "Actual Prevalence (%)") + 
  scale_y_continuous(breaks = c(0,.5,1), labels = c(0, 50, 100), limits = c(-.07, 1.07), name = "Predicted Prevalence (%)") + 
  facet_wrap("pos", ncol = 2, as.table = F) +
  theme(panel.spacing.x = unit(1, "lines")) +
  theme(panel.spacing.y = unit(1, "lines")) + 
  theme(strip.background = element_blank(), strip.text.x = element_text(size = 16, face = "bold"))
}

@@

fullday_long <- function(ds) {
  ds %>% pivot_longer(cols = sit_time:upright_time, names_to = "position", values_to = "prop") %>% 
  mutate(position = factor(position,
                           levels = c("upright_time", "sit_time", "prone_time", "supine_time", "held_time"),
                           labels = c("Upright", "Sitting", "Prone", "Supine", "Held"))) %>% 
  arrange(position, age)
}

>>>>

# PART 2 AGREEMENT
pt2_group <- read_csv("data/compiled_agreement_position.csv") %>% 
  filter(nap_period == 0 & exclude_period == 0 & !is.na(code) & !is.na(pos)) %>% 
         mutate(pos = factor(pos, levels = pos_levels),
                code = factor(code, levels = pos_levels)) %>% 
  filter(file != "104/1")
pt2_split <- read_csv("data/compiled_agreement_split.csv") %>% 
  filter(nap_period == 0 & exclude_period == 0 & !is.na(code) & !is.na(pos)) %>% 
         mutate(pos = factor(pos, levels = pos_levels),
                code = factor(code, levels = pos_levels)) %>% 
  filter(file != "104/1")

@@

# Count up position totals and join into an agreement data frame
calculate_agreement <- function(ds) {
  model <- ds %>% count(file, pos) %>% 
    add_count(file, wt = n, name = "total") %>% 
    mutate(prop_model = n/total)
  human <- ds %>% count(file, code) %>% 
    add_count(file, wt = n, name = "total") %>% 
    mutate(prop_human = n/total)
  agree_group <- full_join(select(model, file, pos, prop_model), 
                     select(human, file, code, prop_human), 
                     by = c("file" = "file", "pos" = "code"))
  agree_group <- agree_group %>% mutate(prop_human = ifelse(is.na(prop_human), 0, prop_human),
                            prop_model = ifelse(is.na(prop_model), 0, prop_model))
  agree_group <- complete(agree_group, file, pos, fill = list(prop_human = 0, prop_model = 0))

}

@@

agreement_scatter <- function(ds) {
  ggplot() +
  geom_point(data = filter(ds, file %in% outlier_files), mapping = aes(x = prop_human, y = prop_model, shape = file, fill = pos), fill = "#333333", size = 4, alpha = .5) + 
  geom_point(data = filter_outliers(ds), mapping = aes(x = prop_human, y = prop_model, fill = pos), shape = 21, alpha = .5, size = 4) + 
  geom_abline(intercept = 0, slope = 1) + 
  scale_fill_manual(values = pal, guide = "none") + 
  scale_shape_manual(guide = "none", values = 22:23) + 
  scale_x_continuous(breaks = c(0,.5,1), labels = c(0, 50, 100), limits = c(-.07, 1.07), name = "Actual Prevalence (%)") + 
  scale_y_continuous(breaks = c(0,.5,1), labels = c(0, 50, 100), limits = c(-.07, 1.07), name = "Predicted Prevalence (%)") + 
  facet_wrap("pos", ncol = 2, as.table = T) +
  theme(panel.spacing.x = unit(1, "lines")) +
  theme(panel.spacing.y = unit(1, "lines")) + 
  theme(strip.background = element_blank(), strip.text.x = element_text(size = 16, face = "bold"))
}

@@

fullday_long <- function(ds) {
  ds %>% pivot_longer(cols = sit_time:upright_time, names_to = "position", values_to = "prop") %>% 
  mutate(position = factor(position, levels = c("supine_time", "prone_time", "sit_time", "upright_time", "held_time"), labels = c("Supine", "Prone", "Sitting", "Upright", "Held"))) %>% 
  arrange(position, age)
}

### 2023-03-14 manuscript.tex
consistent factor orders

\begin{tabular}{lllll}
\toprule
 & \multicolumn{2}{c}{With Outliers} & \multicolumn{2}{c}{Without Outliers} \\
\cmidrule(r){2-3} \cmidrule(r){4-5}
Position & Group & Individual & Group & Individual\\
\midrule
Held & 0.02 & 0.04 & 0.73 & 0.60\\
Prone & 0.97 & 0.86 & 0.97 & 0.84\\
Sitting & 0.79 & 0.97 & 0.91 & 0.95\\
Supine & 0.88 & 0.98 & 0.94 & 0.97\\
Upright & 0.63 & 0.83 & 0.99 & 0.95\\ \midrule
Overall & 0.80 & 0.91 & 0.95 & 0.96\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllll}
\toprule
 & \multicolumn{2}{c}{With Outliers} & \multicolumn{2}{c}{Without Outliers} \\
\cmidrule(r){2-3} \cmidrule(r){4-5}
Position & Group & Individual & Group & Individual\\
\midrule
Held & 0.51 & 0.46 & 0.67 & 0.63\\
Prone & 0.96 & 0.90 & 0.96 & 0.89\\
Sitting & 0.72 & 0.93 & 0.89 & 0.92\\
Supine & 0.76 & 0.96 & 0.88 & 0.93\\
Upright & 0.91 & 0.93 & 0.98 & 0.96\\ \midrule
Overall & 0.80 & 0.94 & 0.92 & 0.94\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllll}
\toprule
 & \multicolumn{2}{c}{Group} & \multicolumn{2}{c}{Individual} \\
\cmidrule(r){2-3} \cmidrule(r){4-5}
Position & Younger & Older & Younger & Older\\
\midrule
Upright & 7.7\% (9.3) & 18.6\% (7.4) & 10.4\% (13.6) & 18.7\% (8.4)\\
Sitting & 25.4\% (12.4) & 44.4\% (10.1) & 18.8\% (16.3) & 46.9\% (13.3)\\
Prone & 14.5\% (13.8) & 14.4\% (6.0) & 12.5\% (10.2) & 16.9\% (10.6)\\
Supine & 38.5\% (24.0) & 14.0\% (8.4) & 40.2\% (31.6) & 10.0\% (9.5)\\
Held & 13.1\% (7.4) & 8.5\% (5.4) & 17.1\% (20.8) & 7.4\% (7.6)\\
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{lllll}
\toprule
 & \multicolumn{2}{c}{With Outliers} & \multicolumn{2}{c}{Without Outliers} \\
\cmidrule(r){2-3} \cmidrule(r){4-5}
Position & Group & Individual & Group & Individual\\
\midrule
Supine & 0.88 & 0.98 & 0.94 & 0.97\\
Prone & 0.97 & 0.86 & 0.97 & 0.84\\
Sitting & 0.79 & 0.97 & 0.91 & 0.95\\
Upright & 0.63 & 0.83 & 0.99 & 0.95\\
Held & 0.02 & 0.04 & 0.73 & 0.60\\ \midrule
Overall & 0.80 & 0.91 & 0.95 & 0.96\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllll}
\toprule
 & \multicolumn{2}{c}{With Outliers} & \multicolumn{2}{c}{Without Outliers} \\
\cmidrule(r){2-3} \cmidrule(r){4-5}
Position & Group & Individual & Group & Individual\\
\midrule
Supine & 0.76 & 0.96 & 0.88 & 0.93\\
Prone & 0.96 & 0.90 & 0.96 & 0.89\\
Sitting & 0.72 & 0.93 & 0.89 & 0.92\\
Upright & 0.91 & 0.93 & 0.98 & 0.96\\
Held & 0.51 & 0.46 & 0.67 & 0.63\\ \midrule
Overall & 0.80 & 0.94 & 0.92 & 0.94\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllll}
\toprule
 & \multicolumn{2}{c}{Group} & \multicolumn{2}{c}{Individual} \\
\cmidrule(r){2-3} \cmidrule(r){4-5}
Position & Younger & Older & Younger & Older\\
\midrule
Supine & 38.5\% (24.0) & 14.0\% (8.4) & 40.2\% (31.6) & 10.0\% (9.5)\\
Prone & 14.5\% (13.8) & 14.4\% (6.0) & 12.5\% (10.2) & 16.9\% (10.6)\\
Sitting & 25.4\% (12.4) & 44.4\% (10.1) & 18.8\% (16.3) & 46.9\% (13.3)\\
Upright & 7.7\% (9.3) & 18.6\% (7.4) & 10.4\% (13.6) & 18.7\% (8.4)\\
Held & 13.1\% (7.4) & 8.5\% (5.4) & 17.1\% (20.8) & 7.4\% (7.6)\\
\bottomrule
\end{tabular}
